Spá: a web-based viewer for text mining in Evidence Based Medicine

### 2014-04-15 documentation/paper.tex
s/pipelines/topologies/

\section{Architecture overview}
\label{section:architecture}
\begin{figure}[htb]
\centering
\includegraphics[width=.9\linewidth]{./diagrams/sequence.pdf}
\caption{\label{fig:sequence}Sequence diagram of a typical request-response}
\end{figure}
Spá relies on Mozilla pdf.js\footnote{\url{http://mozilla.github.io/pdf.js}} for visualization of the document and text extraction.
The results of the text extraction are processed server-side by a variety of pipelines, as outlined in figure \ref{fig:sequence}.
Results from these pipelines, which could be complicated machine learning systems, are communicated back to the browser and displayed using React components\footnote{\url{http://facebook.github.io/react}}.

@@

However, we believe the tool to be useful for a much wider range of text mining and machine learning applications.
To increase the generality of the tool work is being done to support a consumer/producer protocol for the pipelines, allowing developers to quickly plug in new systems.
Furthermore, work is being done on allowing users to save selected annotations, possibly embedded within the document itself, for sharing and off-line use.

>>>>

\section{Architecture overview}
\label{section:architecture}
\begin{figure}[htb]
\centering
\includegraphics[width=.9\linewidth]{./diagrams/sequence.pdf}
\caption{\label{fig:sequence}Sequence diagram of a typical request-response}
\end{figure}
Spá relies on Mozilla pdf.js\footnote{\url{http://mozilla.github.io/pdf.js}} for visualization of the document and text extraction.
The results of the text extraction are processed server-side by a variety of processing topologies, as outlined in figure \ref{fig:sequence}.
Results, which could come from complicated machine learning systems, are communicated back to the browser and displayed using React components\footnote{\url{http://facebook.github.io/react}}.

@@

However, we believe the tool to be useful for a much wider range of text mining and machine learning applications.
To increase the generality of the tool work is being done to support a pluggable system for processing topologies, allowing developers to quickly plug in new systems.
Furthermore, work is being done on allowing users to save selected annotations, possibly embedded within the document itself, for sharing and off-line use.
